%-------------------------
% Resume in Latex
% Author : Jeegn Dani
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{comment}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\Item}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\resumeItem}[2]{\item\small{\textbf{#1}{: #2 \vspace{-2pt}}}}
\newcommand{\resumeSubheading}[4]{\vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Huge Jeegn Dani}} & Email: \href{mailto:jeegndani1604@gmail.com}{jeegndani1604@gmail.com} \\
  {\href{http://linkedin.com/in/jeegndani}{LinkedIn} $\mid$ \href{https://github.com/jeegn}{GitHub}} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University}{West Lafayette, IN}
      {Masters of Science in Computer Science; GPA: 3.9}{Aug. 2023 -- May. 2025}
    \resumeSubheading
      {Purdue University}{West Lafayette, IN}
      {Bachelor of Science in Computer Science and Data Science; GPA: 4.00}{Aug. 2019 -- May. 2023}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Purdue University - Dept. of Computer Science}{West Lafayette, IN}
      {Graduate Teaching Assistant}{Jun. 2021 - Present}
      \resumeItemListStart
        \resumeItem{Courses Taught}
          {Database Systems, Data Structures \& Algorithms, Intro to Data Science, Discrete Math}
        \resumeItem{Autograder Development}
  {Developed an automated autograding system for Relational Algebra (Python, SQL), reducing grading workload by 20+ hours per week. Integrated real-time feedback, streamlining student submissions and assessment}
        \Item{Conducted a comprehensive data-driven analysis with Prof. Hisham Benotman, examining grading consistency across 200+ assessments, revealing a 25\% increase in reliability with autograding compared to manual grading.}
        \Item{Designed and graded exams, assignments, and projects, while conducting weekly recitations (~50 students per session) and leading help sessions on coursework, programming tutorials, and exam preparation.}
      \resumeItemListEnd
      
\resumeSubheading{\href{https://corallab.net/people}{Cognitive Robot Autonomy \& Learning Lab (CoRAL)}}{West Lafayette, IN}
{Software Engineer}{Jan. 2022 – Oct. 2023}
\resumeItemListStart
\resumeItem{Multi-Agent Neural Rearrangement Planning (MANER)}
{Designed a PyBullet-based simulation framework for multi-agent object rearrangement in cluttered environments.}
\Item{Developed a real-time Linux-based communication system to bridge simulations with physical robot experiments.}
\Item{Customized Raspberry Pi-controlled robots for warehouse automation research, enhancing real-world applicability.}
\Item{Published in IEEE Robotics and Automation Letters – \href{https://arxiv.org/pdf/2306.06543.pdf}{[https://arxiv.org/pdf/2306.06543.pdf]}.}
\resumeItemListEnd

    \resumeSubheading
      {\href{https://www.purdue.edu/discoverypark/duri/}{Discovery Undergraduate Interdisciplinary Research Internship}}{West Lafayette, IN}
      {Machine Learning Research Assistant}{Jun. 2021 - Dec. 2021}
      \resumeItemListStart
        \Item{Built an RShinyApp to assist correctional facilities in predicting reoffense rates among drug offenders.}
        \Item{Trained and compared ML models (Logistic Regression, Decision Trees, XGBoost, Neural Networks) for interpretability and fairness.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart

\resumeSubItem{Self-Supervised Learning for Remote Sensing}{}
\begin{itemize}
\item Investigated self-supervised pretraining methods (contrastive learning, masked autoencoders) for satellite imagery.
\item Built a diverse land cover dataset (Google Earth Engine) improving geographic representation for satellite ML models, enhancing model robustness across varied regions.
\item Evaluated state-of-the-art methods such as SeCo, SatMAE, CROMA, and PRESTO for temporal and multispectral learning on both existing and the newly created dataset.
\end{itemize}

    \resumeSubItem{AWS Microservices Migration}{}
\begin{itemize}
\item Refactored a monolithic Django CRUD app into containerized microservices, modularizing code and databases.
\item Deployed it on AWS EC2 and microservices on ECS/EKS with ECR, hosting the frontend on S3 with CDN.
\end{itemize}

    \resumeSubItem{LLVM Compiler}{Developed an LLVM-based compiler in C++, focusing on middle-end optimizations like dead code elimination, loop detection, speculative loop unrolling, and SSA-based register allocation.}

  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{\textbf{Languages \& Technologies}: Python, C, C++, Java, SQL, PyTorch, TensorFlow, AWS, Docker, Kubernetes, Linux, Django, LaTex}
   \item{\textbf{Graduate Coursework}: Deep Learning, Probabilistic ML, Computer Vision, NLP, Statistical ML, Robotics, Cloud Computing, Analysis of Algorithms, Compilers, Information Security.}
 \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}